Article Title

### 2013-09-24 plos.tex
included figure5.
minor corrections
Kreso's comments
Added Author Summary
minor edits

\DeclareMathOperator{\Tr}{tr}
\newcommand{\mcond}{\,\middle\vert\,}
\newcommand{\cond}{\,\vert\,}
\newcommand{\T}{\intercal}
\newcommand{\TODO}[1]{\emph{\tiny\color{blue}$\langle\langle$#1$\rangle\rangle$}}
\newcommand*\dif{\mathop{}\,d}

@@

% Title must be 150 characters or less
\begin{flushleft}
{\Large
Improved estimates of neural correlations suggest detailed interactions in visual cortex
}
% Insert Author names, affiliations and corresponding author email.
\\
Dimitri Yatsenko$^{1,\ast}$, 
Alexander Ecker$^{2,1}$,
Emmanouil Foudarakis$^{1}$,
R.~James Cotton$^{1}$,
Kre\v{s}imir Josi\'{c}$^{3}$,
Andreas S.~Tolias$^{1}$
\\
\bf{1} Department of Neuroscience, Baylor College of Medicine, Houston, TX, USA
\\
\bf{2} Max Planck Institute of Biological Cybernetics, T\"ubingen, Germany
\\
\bf{3} Department of Mathematics and Department of Biology and Biochemistry, University of Houston, Houston, TX, USA
\\
$\ast$ E-mail: yatsenko@cns.bcm.edu
\end{flushleft}

@@

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLoS ONE authors please skip this step. 
% Author Summary not valid for PLoS ONE submissions.   
\section*{Author Summary}

@@

\subsection*{Subsection 1}

\subsection*{Subsection 2}

\section*{Discussion}

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Theory of covariance estimation}
\input{sections/Theory.tex}
\input{sections/Estimators.tex}
\input{sections/Simulation.tex}

@@

\section*{Figure Legends}
%\begin{figure}[!ht]
%\begin{center}
%%\includegraphics[width=4in]{figure_name.2.eps}
%\end{center}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
%should be left justified, as specified by the options to the caption 
%package.
%}
%\label{Figure_label}
%\end{figure}

\section*{Tables}
%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}
% \end{table}

>>>>

\DeclareMathOperator{\Tr}{tr}
\newcommand{\mcond}{\,\middle\vert\,}
\newcommand{\cond}{\,\vert\,}
\newcommand{\T}{\intercal}
\newcommand{\TODO}[1]{\emph{\small\color{blue}$\langle\langle$#1$\rangle\rangle$}}
\newcommand*\dif{\mathop{}\,d}

@@

% Title must be 150 characters or less
\begin{flushleft}
{\Large
Improved estimates of neural correlations suggest detailed interactions in visual cortex
}
% Insert Author names, affiliations and corresponding author email.
\\
Dimitri Yatsenko$^{1,\ast}$, 
Kre\v{s}imir Josi\'{c}$^{2}$,
Alexander Ecker$^{3,1}$,
Emmanouil Foudarakis$^{1}$,
R.~James Cotton$^{1}$,
Andreas S.~Tolias$^{1}$
\\
\bf{1} Department of Neuroscience, Baylor College of Medicine, Houston, TX, USA
\\
\bf{2} Max Planck Institute of Biological Cybernetics, T\"ubingen, Germany
\\
\bf{3} Department of Mathematics and Department of Biology and Biochemistry, University of Houston, Houston, TX, USA
\\
$\ast$ E-mail: yatsenko@cns.bcm.edu
\end{flushleft}

@@

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLoS ONE authors please skip this step. 
% Author Summary not valid for PLoS ONE submissions.   
\section*{Author Summary}
\input{sections/Summary.tex}

@@

\section*{Discussion}
%\input{sections/Discussion.tex}

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}

@@

\section*{Figure Legends}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=4in]{figures/Figure1.pdf}
\end{center}
\caption{
{\bf Acquistion of neural population activity using two-photon fluorescence imaging of calcium signal.}  {\tt A.} Visual stimuli comprising full-field  
}
\label{Figure_label}
\end{figure}

%\section*{Tables}
%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}
% \end{table}

### 2013-09-24 sections/Results.tex
minor edits

The usual estimator of $\Sigma$ is the sample covariance matrix
\begin{equation}
\hat \Sigma_0 = \frac 1 {n-c} \sum\limits_{t=1}^T (x(t)-\mu)(x(t)-\mu)^\T 
\end{equation}
where $x(t),\;t=1,\ldots,n$ are sequential observations of population activity inferred from calcium signals. Bessel's correction $c$ makes the estimate unbiased such that $\mathbb E[\Sigma_0] = \Sigma$. When observations $x(t)$ can be assumed to be independent then $c=1$; but when observations are correlated $c>1$ may be estimated from the data.

\subsubsection*{Regularization}
Although $\hat\Sigma_0$ is unbiased, it is not necessarily as close as possible to $\Sigma$.  Closer estimates can be produced by admitting a moderate amount of bias (\emph{approximation error}) in order to reduce the variance (\emph{estimation error}) of the estimate.

Regularization is the deliberate biasing of the unbiased estimate toward a low-dimensional target estimate in order to strike a favorable balance between bias and variance and minimize the overall expected error. \cite{Bickel:2006,

>>>>

The usual estimator of $\Sigma$ is the sample covariance matrix
\begin{equation}
\hat \Sigma_0 = \frac 1 {n-c} \sum\limits_{t=1}^n (x(t)-\mu)(x(t)-\mu)^\T 
\end{equation}
where $x(t),\;t=1,\ldots,n$ are sequential observations of population activity inferred from calcium signals. Bessel's correction $c$ makes the estimate unbiased such that $\mathbb E[\hat\Sigma_0] = \Sigma$. When observations $x(t)$ can be assumed to be independent then $c=1$; but when observations are correlated $c>1$ may be estimated from the data.

\subsubsection*{Regularized estimates}
Although $\hat\Sigma_0$ is unbiased, it is not as close as possible to $\Sigma$.  Closer estimates can be produced by admitting a moderate amount of bias (\emph{approximation error}) in order to reduce the variance (\emph{estimation error}) of the estimate. 
\emph{Regularization} is the deliberate biasing of the estimate toward a low-dimensional target estimate in order to strike a favorable balance between bias and variance and minimize the overall expected error \cite{Bickel:2006,Ledoit:2004}.
